---
title: "Sliding D4 Window"
author: "Zach Diener"
date: "June 17, 2015"
output: html_document
---

```{r}
library(wavethresh)
library(gplots)
library(wavelets)

rm(list=ls())	#Clear data

sds<-sample(rep(c(0,0.2,0.4,0.6,0.8,1.0,1.2,1.4,1.6,1.8,2.0),30))	#Generate random list of standard deviations
TestCases<-data.frame(matrix(NA,nrow=330,ncol=70))	#Create empty data frame to store simulated signals
NoiseSeeds<-data.frame(matrix(NA,nrow=330,ncol=626))	#Create empty data frame to store state of RNG before each injection of noise
SD_Change<-data.frame(matrix(NA,nrow=330,ncol=2))	#Create empty data frame to store standard deviations and transition points
colnames(SD_Change)<-c("sd","change")	#Name columns 
x<-(1:70)	#Create vector of values from 1 to 70
for(i in 1:330){	#Loop over all standard deviations
		change1<-sample(25:55,1)	#Randomly select transition point between 25 and 55
		NoiseSeeds[i,]<-.Random.seed	#Store state of RNG
		TestCases[i,(1:70)]<-(((x>=1 & x<(change1-25))*0)+((x>=(change1-25) & x<(change1-10))*((0.02*x)+0.5-(0.02*change1)))+((x>=(change1-10) & x<(change1-6))*(x+10.3-change1))+((x>=(change1-6) & x<(change1))*(4.3))+((x>=(change1) & x<(change1+10))*((-0.5*x)+4.3+(0.5*change1)))+((x>=(change1+10) & x<=(change1+15))*((-0.25*x)+1.8+(0.25*change1)))+((x>(change1+15) & x<=1000)*(-1.95)))+rnorm(length(x),sd=sds[i])+20	#Inject noise into base signal and store
	#	TestCases[i,71]<-paste(";",(i),sep="")	#Label signal for later identification
		SD_Change[i,"change"]<-change1	#Store transition point
}	#End loop
SD_Change[,"sd"]<-sds	#Store standard deviation of injected noise
write.csv(NoiseSeeds,row.names=FALSE,"./NoiseSeeds.csv")	#Save output
write.csv(TestCases,row.names=FALSE,"./TestCases.csv")	#Save output
write.csv(SD_Change,row.names=FALSE,"./SD_Change.csv")	#Save output
df <- as.data.frame(read.csv("TestCases.csv", header=T)) # read in data frame

```
#Construct A & D
```{r}
df_1<-as.vector(as.matrix(df[31,]))
numlevels <- 4
signallength <- length(df)

A <- matrix(0,nrow=numlevels,ncol=signallength)
D <- matrix(0,nrow=numlevels,ncol=signallength)

for (i in 1:4) {
  
  f <- wt.filter(filter="d4", modwt=FALSE, level=i)
  a <- convolve(df_1, f@g, conj=FALSE,type="open")
  d <- convolve(df_1, f@h, conj=FALSE,type="open")
 
  A[i,c((((3*(2^(i)-1))+1)-(2^i)):(length(a)-(2^i)-(3*((2^(i))-1))))] <- a[(2*(3*((2^(i))-1))) : (length(a)-1)]
  D[i,c((((3*(2^(i)-1))+1)-(2^i)):(length(d)-(2^i)-(3*((2^(i))-1))))] <- d[(2*(3*((2^(i))-1))) : (length(d)-1)]
   
}

```
#Thresholding
```{r}
Arow_1 <- A[1,2:68]
sigma <- (mad(Arow_1))/.6745
#print(mad(Arow_1))
Thresh<- sigma * (sqrt(2* log(length(Arow_1))))

Amod <- matrix(0,nrow=numlevels,ncol=signallength)
for (i in 1:4) {
  f <- wt.filter(filter="d4", modwt=FALSE, level=i)
  a <- convolve(df_1, f@g, conj=FALSE,type="open")
  Amod[i,c((((3*(2^(i)-1))+1)-(2^i)):(length(a)-(2^i)-(3*((2^(i))-1))))] <- a[(2*(3*((2^(i))-1))) : (length(a)-1)]
}

#Hard Threshold

#for(i in 1:4){
 # b <- Amod[i,] < 30
 # Amod[i,b] <- (Amod[i,b] <- 0) 
#}

#Soft Threshold

for (i in 1:4){
  high <- Amod[i,] >= Thresh
  mid <- Amod[i,] < Thresh
  low <- Amod[i,] <= -Thresh
  Amod[i,high] <- (Amod[i,high] <- (Amod[i,high]-Thresh))
  Amod[i,mid] <- (Amod[i,mid] <- 0)
  Amod[i,low] <- (Amod[i,low] <- (Amod[i,low]+Thresh))
}


```

options(digits=3)
# averages
A

# differences
D

D<- abs(D)

image(t(D))

heatmap.2(D,
  main = "Heatmap ",
  xlab = "Time",
  ylab = "Frequency",
  key=T, 
  keysize=1.5, 
  key.title = NA,
  symkey=TRUE, 
  notecol="black",            
  density.info="histogram",     
  trace="none",               
  margins =c(4,3),            
  dendrogram="none",           
  Rowv = FALSE,
  Colv = FALSE,
  srtCol = 1,
  cexRow = 1.0,
  breaks= 63,
  adjCol = c(0.5,1),
  col= grey.colors(62, start= 0.9, end=0.1, gamma=.7)
  )

plot(df_1, main = "Simulation Data", xlab= "Time", ylab="Brightness Level", xlim=c(7,70), ylim= c(14,28),type = "l", col = "red")

```
